### 2015-07-10 narrative/intro.tex
minor changes again.

% 
Our proposed research program is guided by the following overarching objectives:
\begin{itemize}
\item
{\em Address emerging storage architecture and technology landscape:}
We will address the associated I/O and storage challenges in the context of
current and emerging storage landscapes,
% and expedite insights into critical
%scientific processes, while demonstrating the validity of our approach in key
%DOE domains. 
%We will research techniques for creating and using a Scalable 
%Storage Software Infrastructure, and integrating services from the middleware 
%layer with Storage System capabilities to support 
and will develop novel strategies for distributing 
data both horizontally and vertically across the layers of these storage systems.  
Negotiation between these layers will be provided as a fundamental service, allowing users to
easily save ``the best''  data, which is automatically placed throughout the
entire storage stack.
\item
{\em Develop a science driven, system aware approach:}
%Our approach targets the expected characteristics of exascale storage hardware.
%The storage layer will be partitioned into multiple heterogeneous tiers with
%vastly different performance characteristics. The layers will be further
%differentiated by the constraints on capacity and data lifetime within each
%layer. Tape archival storage will still maintain data long term, but access to
%this data will be orders of magnitude slower than the next layer and naively
%accessing data from archival storage will greatly impact productivity.
%
Given that storage systems will be composed of multiple heterogeneous tiers with
vastly different performance characteristics and constraints on capacity and 
supported data lifetime, our approach will enable researchers to 
place more knowledge into the Storage Systems and Input/Output (SSIO) system so that data can be recast from 
a sequence of bytes to information rich data. This information rich data can then
be used by the system to guide the  placement within the tiered storage and will optimize the time
to gain knowledge and insight from exascale simulations.

@@

\item
{\em Emphasize impacts on science:}
%The metric we are most interested in optimizing is time to knowledge.  
%Current approaches to addressing the I/O bottleneck fall into two broad categories:
%parallel file system approaches that optimize the throughput for an entire
%system, and I/O middleware approaches that optimize the performance of a single
%application. Both approaches have been successful to date, but are unlikely to
%overcome the remaining obstacles in reaching exascale. 
Instead of trying to optimize throughput, we will seek to reduce the time to knowledge.
As extracting knowledge is the only metric that matters for scientific applications, we will
focus not only upon data storage, but upon efficient  retrieval of knowledge from their 
workflows.
Moreover, we aim to perform the optimization not only for a single
application, but rather for multiple workloads running on a multi-user, multi-application
system.
\end{itemize}

@@

6 & Approaches to improve the ability of SSIO software to support checkpoint/restart & We will have utility functions defined for the lifetime of data, and allow CR data to be automatically placed in the fastest storage and then purged when it is no longer needed & \S \ref{fig:ssio-bucket}, \S\ref{sec:qos}, \S\ref{sec:managing-data-life}  \\
\hline
\end{tabular}
\end{center}
\vskip -0.5cm
\end{table}

@@

\paragraph{Simulation Perspective}
\label{subsec:sim-perspective}
The simulation scientist ideally should be able to
obtain an estimate of how much time will be required to write the data,
and how much storage space is available during the simulations lifetime.
Further, they would like Quality of Service (QoS) assurances so that reactions
to varying bandwidth can be handled appropriately. Ideally, a set of
user-specified rules would allow the system to make autonomic decisions dynamically.
%

Central to our approach is giving users the ability to define the importance, or utility of their data.
This includes the ability to assign varying levels of importance to individual data objects in their entirety, or specific
subsets and pieces.
Research challenges include: 1) an expressive and easy to use interface, 2) a model for the system supporting
autonomic decision for saving data using the user-defined importance and utility of data, and 3) the interface between
the system and the back-end storage across both single, and multiple running applications.

>>>>

% 
Our proposed research program is guided by the following overarching objectives:
\begin{tightItemize}
\item
{\em Address emerging storage architecture and technology landscape:}
We will address the associated I/O and storage challenges in the context of
current and emerging storage landscapes,
% and expedite insights into critical
%scientific processes, while demonstrating the validity of our approach in key
%DOE domains. 
%We will research techniques for creating and using a Scalable 
%Storage Software Infrastructure, and integrating services from the middleware 
%layer with Storage System capabilities to support 
and will develop novel strategies for distributing 
data both horizontally and vertically across the layers of these storage systems.  
Negotiation between these layers will be provided as a fundamental service, allowing users to
easily save ``the best''  data, which is automatically placed throughout the
entire storage stack.
\item
{\em Develop a science driven, system aware approach:}
%Our approach targets the expected characteristics of exascale storage hardware.
%The storage layer will be partitioned into multiple heterogeneous tiers with
%vastly different performance characteristics. The layers will be further
%differentiated by the constraints on capacity and data lifetime within each
%layer. Tape archival storage will still maintain data long term, but access to
%this data will be orders of magnitude slower than the next layer and naively
%accessing data from archival storage will greatly impact productivity.
%
Given that storage systems will be composed of multiple heterogeneous tiers with
vastly different performance characteristics and constraints on capacity and 
supported data lifetime, our approach will enable researchers to 
place more knowledge into the Storage Systems and Input/Output (SSIO) system so that data can be recast from 
a sequence of bytes to information rich data. This information rich data can then
be used by the system to guide the  placement within the tiered storage and will optimize the time
to gain knowledge and insight from exascale simulations.

@@

\item
{\em Emphasize impacts on science:}
%The metric we are most interested in optimizing is time to knowledge.  
%Current approaches to addressing the I/O bottleneck fall into two broad categories:
%parallel file system approaches that optimize the throughput for an entire
%system, and I/O middleware approaches that optimize the performance of a single
%application. Both approaches have been successful to date, but are unlikely to
%overcome the remaining obstacles in reaching exascale. 
Instead of trying to optimize throughput, we will seek to reduce the time to knowledge.
As extracting knowledge is the only metric that matters for scientific applications, we will
focus not only upon data storage, but upon efficient  retrieval of knowledge from their 
workflows.
Moreover, we aim to perform the optimization not only for a single
application, but rather for multiple workloads running on a multi-user, multi-application
system.
\end{tightItemize}

@@

6 & Approaches to improve the ability of SSIO software to support checkpoint/restart & We will have utility functions defined for the lifetime of data, and allow CR data to be automatically placed in the fastest storage and then purged when it is no longer needed & \S \ref{sec:data-description}, \S\ref{sec:qos}, \S\ref{sec:managing-data-life}  \\
\hline
\end{tabular}
\end{center}
\vskip -0.5cm
\end{table}

@@

\paragraph{Simulation Perspective}
\label{subsec:sim-perspective}
The simulation scientist ideally should be able to
obtain an estimate of how much time will be required to write the data,
and how much storage space is available during the simulations lifetime.
Further, they would like Quality of Service (QoS) assurances so that reactions
to varying bandwidth can be handled appropriately. Ideally, a set of
user-specified rules would allow the system to make autonomic decisions dynamically
~\S~\ref{sec:qos}.
%

Central to our approach is giving users the ability to define the importance, or utility of their data    
 \S\ref{sec:data-description}.
This includes the ability to assign varying levels of importance to individual data objects in their entirety, or specific
subsets and pieces.
Research challenges include: 1) an expressive and easy to use interface, 2) a model for the system supporting
autonomic decision for saving data using the user-defined importance and utility of data~\S~\ref{sec:managing-data-life})
, and 3) the interface between
the system and the back-end storage across both single, and multiple running applications~\S~\ref{sec:qos}.
